A generalized definition of multidimensional item response theory parameters

### 2024-07-24 output/paper_draft/paper_M2PLM_parameters.Rmd
Moves vector and coordinate equivalence earlier

with $`r DISCR_COORDS_ALT_EQ`$, and
$`r TRANSFORM_MATRIX_TRANSP_INV`$ a change of basis matrix.
Note that $`r TRANSFORM_MATRIX_TRANSP_INV`$ determines $`r TEST_SPACE_BASIS`$.

@@

\begin{equation}
  `r SLOPE_MAX_STD_COSINES_EQ`.                     (\#eq:slope-max-std-cosines)
\end{equation}

As $`r DISCR_VECTOR`$ is defined in space $`r TEST_SPACE`$ with basis
$`r TEST_SPACE_BASIS`$, its algebraic vector values correspond to its
coordinates, i.e., $`r DISCR_VECTOR_COORDS_EQ`$. Therefore, by Equation
\@ref(eq:discr-vector-std),

>>>>

with $`r DISCR_COORDS_ALT_EQ`$, and
$`r TRANSFORM_MATRIX_TRANSP_INV`$ a change of basis matrix.
Note that $`r TRANSFORM_MATRIX_TRANSP_INV`$ determines $`r TEST_SPACE_BASIS`$
and, as $`r DISCR_VECTOR`$ is expressed in this basis,
its algebraic vector values correspond to its coordinates, i.e.,
$`r DISCR_VECTOR_COORDS_EQ`$.

@@

\begin{equation}
  `r SLOPE_MAX_STD_COSINES_EQ`                      (\#eq:slope-max-std-cosines)
\end{equation}

and, by Equation \@ref(eq:discr-vector-std),
